### 2025-02-04 Paper/computers&geosiciences/CAGEO_LaTeXTemplate-main/manuscript.tex
ete

\section{Methodology}
Creating the dataset is a big problem for classification or segmentation processes. In this study, Unmanned Air Vehicle (UAV) was used to collect data. An orthophoto image of the region was created from aerial photographs obtained by UAV.Model building processes were conducted in a part of the study area. Training and testing images were generated from this region. Rock blocks were labeled, and mask images were created. The segmentation process was then carried out using Python and necessary libraries, and the results were converted into polygon vector files. Additionally, the volumes and 3D surface areas of all the rocks were calculated (Fig. \ref{fig:Figure3}).

>>>>

\section{Methodology}
Creating the dataset is a big problem for classification or segmentation processes. In this study, Unmanned Air Vehicle (UAV) was used to collect data. An orthophoto image of the region was created from aerial photographs obtained by UAV. Model building processes were conducted in a part of the study area. Training and testing images were generated from this region. Rock blocks were labeled, and mask images were created. The segmentation process was then carried out using Python and necessary libraries, and the results were converted into polygon vector files. Additionally, the volumes and 3D surface areas of all the rocks were calculated (Fig. \ref{fig:Figure3}).
